### 2017-07-20 src/5_2_Proposal.tex
details only

    \node (pro4a) [process, right of=dec2, xshift=4cm] {$v = \texttt{Johansen}(\mathbf{y}_i,p)$ \\
                                                        $\mathbf{A} = \texttt{uvecm}(\mathbf{y}_i,p,v,\mathbf{A})$ \\
                                                        $\mathbf{X} = \texttt{OLS} (\mathbf{A},\mathbf{B})$};

>>>>

    \node (pro4a) [process, right of=dec2, xshift=4cm] {$v = \texttt{Johansen}(\mathbf{y}_i,p)$ \\
                                                        $\mathbf{A} = \texttt{ovecm}(\mathbf{y}_i,p,v,\mathbf{A})$ \\
                                                        $\mathbf{X} = \texttt{OLS} (\mathbf{A},\mathbf{B})$};

### 2017-07-20 src/5_3_Proposal.tex
details only

VECM model parameters are traditionally obtained using ordinary least squares
(OLS) method. OLS has two main problems: is sensitive to errors on input data
and involves many calculations. The former problem is commonly solved using
Ridge Regression (RR) \cite{hoerl1970} which introduces a regularization
parameter that leads to an unbiased estimation with better generalization
capability. The second problem of computational complexity depends on the number
of past values and observations considered.  Recently, online learning
algorithms have been proposed to solve problems with large data sets because of
their simplicity and their ability to update the model when new data is
available.

The proposal is to modify OVECM so it wan be an incremental algorithm and also
to use RR and its variant AAR instead of OLS. Therefore, three different
variations of OVECM using as a solver: OLS, RR and AAR will be compared.

@@

Since financial problems are stream data problems, it is unfeasible to include
all input data in a VECM model. Our proposal consists on an online version of
VECM (OVECM) capable of updating the model with new arrival data and give
responses in a short period of time. OVECM only considers a time varying window
of historical data and the using of RR or its variant AAR (Aggregating Algorithm
for Regression) as an alternative of OLS to get model parameters.

On the other hand, getting cointegration vectors using Johansen method is also a
computationally expensive procedure. However, since cointegration vectors
represent the long-run relationship between the time series, they vary little in
time. This proposal also include to obtain new cointegration vectors only when
this long-term relationship changes. This change is detected by tracking the
Mean Absolute Percentage Error (MAPE) of the last $n$ in-sample forecasts.

%Since VECM is a model based on time series differences, the MAPE is obtained
%from $\Delta \mathbf{y}$ as following:
% 
%\begin{equation}\label{eq:MAPE}
%\text{MAPE}[t] = \frac{1}{n} \sum_{i=1}^{n} \left| 
%\frac{\Delta \mathbf{y}_{\text{true}}[t-i]-\Delta
%\mathbf{y}_{\text{pred}}[t-i]}{\Delta \mathbf{y}_{\text{true}[t-i]}}
%\right| \, , 
%\end{equation}
%
%\noindent where $\Delta \mathbf{y}_{\text{true}}$ is the actual value of the
%time series $\mathbf{y}$ differences and $\Delta \mathbf{y}_{\text{pred}}$ is
%their forecast value.

%The method proposed consists of
%a modification of RR considering a sliding window which contains only
%the last $L$ samples %and the new input $\mathbf{x}_t$, 
%i.e. $\{\mathbf{x}_i\}_{i=t-L+1}^{t-1}$.

VECM($p$) was defined in equation \ref{eq:vecfull} and its matrix form is:

@@

\noindent where matrix $\mathbf{B}$ is defined in equation
\ref{eq:vecY}, matrix $\mathbf{X}$ is detailed in equation \ref{eq:vecX}, matrix
$\mathbf{E}$ in equation \ref{eq:vecE} and matrix $\mathbf{A}$ in equation \ref{eq:vecA}.

>>>>

VECM model parameters are traditionally obtained using ordinary least squares
(OLS) method. OLS has two main problems: is sensitive to input data errors
and involves many calculations. The former problem is commonly solved using
Ridge Regression (RR) \cite{hoerl1970} which introduces a regularization
parameter that leads to an unbiased estimation with better generalization
capability. The second problem of computational complexity depends on the number
of past values and observations considered.  Recently, online learning
algorithms have been proposed to solve problems with large data sets because of
their simplicity and their ability to update the model when new data is
available.

The proposal is to create an online algorithm based on the idea of OVECM
using either RR or its variant AAR instead of OLS 
.

@@

OVECM only considers a time varying window of historical data and uses OLS to
get solve model parameters. This proposal is about using RR or its variant AAR
as an alternative of OLS to get model parameters.

Since cointegration vectors represent a long-run relationship between the time
series, they vary little in time. This proposal also includes to obtain new
cointegration vectors only when this long-term relationship changes. This change
is detected by tracking the Mean Absolute Percentage Error (MAPE) of the last
$n$ in-sample forecasts.

VECM($p$) matrix form is:

@@

\noindent where matrix $\mathbf{B},\mathbf{X},\mathbf{E}$ and $\mathbf{A}$ were
previously defined in equations \ref{eq:vecY} , \ref{eq:vecX} , \ref{eq:vecE} and
\ref{eq:vecA} respectively.
